Large squeezing in multicomponent trapped Bose-Einstein condensates

### 2013-06-11 large_number_squeezing_with_atoms.tex
Minor changes.

To minimise the damaging effects of the non-zero momentum modes it is better to operate in a regime where the total occupation of the non-zero momentum modes $N_{\mathbf{k}\neq 0}$ is small, which is also fortuitously the regime in which the Bogoliubov theory is a good approximation.  To better understand when $N_{\mathbf{k}\neq 0}/N$ can be expected to be small, we approximate the sum in \eqref{eqCondensateDepletion} with an integral.  In 1D Eq.~\eqref{eqCondensateDepletion} is
\begin{align}
  \frac{N_{\mathbf{k}\neq 0}(t)}{N} &= \frac{(n_a \chi_{aa} \tau_\text{hold} \cos\theta)^2}{N} \sum_{k \neq 0} \sinc^2\left(\sqrt{\omega^0_{k}(\omega^0_{k}+2 \chi_{aa}n_a)}\tau_\text{hold}\right).
\end{align}
We wish to approximate this sum by the integral
\begin{align}
  \frac{N_{\mathbf{k}\neq 0}(t)}{N} &\approx \frac{(n_a \chi_{aa} \tau_\text{hold} \cos\theta)^2}{N} \int_{-\infty}^{+\infty} \sinc^2 \left(\sqrt{\omega^0_{k}(\omega^0_{k}+2 \chi_{aa}n_a)}\tau_\text{hold}\right) \frac{d k}{\Delta k}, \label{eqCondensateDepletionFirstIntegralApproximation}
\end{align}
where $\Delta k = 2\pi/L$.  This approximation will be valid in the limit that $\omega_{k_\text{min}} \tau_\text{hold} \ll 1$, where $k_\text{min} = 2\pi/L$ as for small $k$ the allowed values $k = n_x 2\pi /L$ will closely sample the region $\xi = \sqrt{\omega_k^0(\omega_k^0 + 2 \chi_{aa} n_a)} \tau_\text{hold} < \pi$ where $\sinc^2(\xi)$ is significant.

Changing integration variables to $\Phi = \omega^{0}_{\mathbf{k}}\tau_\text{hold}$ and defining $\Lambda_a = n_a \chi_{aa} \tau_\text{hold}$ the expression \eqref{eqCondensateDepletionFirstIntegralApproximation} can be written as
\begin{align}
  \frac{N^\text{1D}_{\mathbf{k}\neq 0}(t)}{N} &\approx \frac{1}{N} \frac{\Lambda_a^2 L \cos^2\theta } {\sqrt{2}\pi\sqrt{\frac{\hbar}{M}\tau_\text{hold}}} f^\text{1D}(\Lambda_a),
\end{align}
where
\begin{align}
  f^\text{1D}(\Lambda) &= \int_0^{\infty} \frac{1}{\sqrt{\Phi}}\sinc^2\sqrt{\Phi(\Phi + 2 \Lambda)}\, d\Phi.
\end{align}
In 2D and 3D the equivalent expressions are
\begin{align}
  \frac{N^{\text{2D}}_{\mathbf{k}\neq 0}(t)}{N} &\approx \frac{1}{N} \frac{\Lambda_a^2 A \cos^2\theta } {4\frac{\hbar}{M}\tau_\text{hold}} f^\text{2D}(\Lambda_a), \\
  \frac{N^{\text{3D}}_{\mathbf{k}\neq 0}(t)}{N} &\approx \frac{1}{N} \frac{\Lambda_a^2 V \cos^2\theta } {\sqrt{2}\pi^2\left(\frac{\hbar}{M}\tau_\text{hold}\right)^{3/2}} f^\text{3D}(\Lambda_a),
\end{align}
where
\begin{align}
  f^\text{2D}(\Lambda) &= \int_0^{\infty} \sinc^2\sqrt{\Phi(\Phi + 2 \Lambda)}\, d\Phi,\\
  f^\text{3D}(\Lambda) &= \int_0^{\infty} \sqrt{\Phi} \sinc^2\sqrt{\Phi(\Phi + 2 \Lambda)}\, d\Phi.
\end{align}

>>>>

To minimise the damaging effects of the non-zero momentum modes it is better to operate in a regime where the total occupation of the non-zero momentum modes $N_{\mathbf{k}\neq 0}$ is small, which is also fortuitously the regime in which the Bogoliubov theory is a good approximation.  To better understand when $N_{\mathbf{k}\neq 0}/N$ will be small, we approximate the sum in \eqref{eqCondensateDepletion} with an integral.  In 1D Eq.~\eqref{eqCondensateDepletion} is
\begin{align}
  \frac{N_{\mathbf{k}\neq 0}(t)}{N} &= \frac{(n_a \chi_{aa} \tau_\text{hold} \cos\theta)^2}{N} \sum_{k \neq 0} \sinc^2\left(\sqrt{\omega^0_{k}(\omega^0_{k}+2 \chi_{aa}n_a)}\tau_\text{hold}\right).
\end{align}
We wish to approximate this sum by the integral
\begin{align}
  \frac{N_{\mathbf{k}\neq 0}(t)}{N} &\approx \frac{(n_a \chi_{aa} \tau_\text{hold} \cos\theta)^2}{N} \int_{-\infty}^{+\infty} \sinc^2 \left(\sqrt{\omega^0_{k}(\omega^0_{k}+2 \chi_{aa}n_a)}\tau_\text{hold}\right) \frac{d k}{\Delta k}, \label{eqCondensateDepletionFirstIntegralApproximation}
\end{align}
where $\Delta k = 2\pi/L$ and $L$ is the length of the 1D box condensate.  This approximation will be valid in the limit that $\omega_{k_\text{min}} \tau_\text{hold} \ll 1$, where $k_\text{min} = 2\pi/L$ as for small $k$ the allowed values $k = n_x 2\pi /L$ will closely sample the region $\xi = \sqrt{\omega_k^0(\omega_k^0 + 2 \chi_{aa} n_a)} \tau_\text{hold} < \pi$ where $\sinc^2(\xi)$ is significant.

Changing integration variables to $\Phi = \omega^{0}_{\mathbf{k}}\tau_\text{hold}$ and defining $\Lambda_a = n_a \chi_{aa} \tau_\text{hold}$ the expression \eqref{eqCondensateDepletionFirstIntegralApproximation} can be written as
\begin{align}
  \frac{N^\text{1D}_{\mathbf{k}\neq 0}(t)}{N} &\approx \frac{1}{N} \frac{\Lambda_a^2 L \cos^2\theta } {\sqrt{2}\pi\sqrt{\frac{\hbar}{M}\tau_\text{hold}}} f^\text{1D}(\Lambda_a),
\end{align}
where
\begin{align}
  f^\text{1D}(\Lambda) &= \int_0^{\infty} \frac{1}{\sqrt{\Phi}}\sinc^2\sqrt{\Phi(\Phi + 2 \Lambda)}\, d\Phi.
\end{align}
In 2D and 3D the equivalent expressions are
\begin{align}
  \frac{N^{\text{2D}}_{\mathbf{k}\neq 0}(t)}{N} &\approx \frac{1}{N} \frac{\Lambda_a^2 A \cos^2\theta } {4\frac{\hbar}{M}\tau_\text{hold}} f^\text{2D}(\Lambda_a), \\
  \frac{N^{\text{3D}}_{\mathbf{k}\neq 0}(t)}{N} &\approx \frac{1}{N} \frac{\Lambda_a^2 V \cos^2\theta } {\sqrt{2}\pi^2\left(\frac{\hbar}{M}\tau_\text{hold}\right)^{3/2}} f^\text{3D}(\Lambda_a),
\end{align}
where
\begin{align}
  f^\text{2D}(\Lambda) &= \int_0^{\infty} \sinc^2\sqrt{\Phi(\Phi + 2 \Lambda)}\, d\Phi,\\
  f^\text{3D}(\Lambda) &= \int_0^{\infty} \sqrt{\Phi} \sinc^2\sqrt{\Phi(\Phi + 2 \Lambda)}\, d\Phi,
\end{align}
and $A$ is the area of the two-dimensional system and $V$ is the volume of the three-dimensional system.
